The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{oblique} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.

>>>>

The main purpose of this study is to use 3D\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{oblique} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
